---
title: "Map OD to Classes"
author: "Boyana Buyuklieva"
date: "December 15, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(foreign)
library(readr)
library(plyr)
library(dplyr)
library(stringr)
```

```{r, cache=T}
flow81 <- read_csv("./_data/1981_SMS_Set2(2001 geog)_noheaders.csv")#4227744

flow81 <- read.csv("C:/Users/billi/Desktop/Ch7/_data/1981_SMS_Set2(2001 geog)_noheaders.csv", header=T)
LUT81 <- read.dbf("./_data/F1981.dbf")

x_codes_1 <- read_csv("./_data/Wards__April_1991__Names_and_Codes_in_the_United_Kingdom.csv")
x_codes_1 <- x_codes_1[,c("WD91CD","WD91CDC","WD91CDO")]
names(x_codes_1 ) <- c("WD91CD","_WD91CDC","_WD91CDO")

x_codes_2 <- read_csv("./_data/LUT_Ward_1981_to_Ward_1991__April_1991__Lookup_in_England_and_Wales.csv")


flow91 <- read_csv("./_data/Flows_1991_by1991wards.csv")
LUT91 <- read.dbf("./_data/F1991.dbf")


flow01 <- read_csv("./_data/SMS_2001_wicid_output_OAs_Destination Pair.csv", skip = 3,  col_names = T)
LUT01 <- read.dbf("./_data/F2001.dbf")

flow11 <- read_csv("./_data/2011/MF01UK_oa_all_v5/mf01uk_oa_all_v5.csv",  col_names = FALSE)
LUT11 <- read.dbf("./_data/F2011.dbf")
```

## 2011

```{r}
flow<- flow11
LUT <- LUT11

#Process the StabDen LUT
LUT$zone_id <- LUT$oa11cd
LUT <- LUT[,c('zone_id','rdl_PSD','lad11nm','rgn11nm')]

LUT$LUT <- paste(LUT$rdl_PSD, "*", LUT$lad11nm, "*", LUT$rgn11nm)
LUT$LUT <- gsub(" ", "", LUT$LUT, fixed = TRUE)


#sum up the year specific breakdowns 
names(flow) <- c("O","D","Count")
simple_flow <- cbind(flow$O,flow$D, flow$Count)
backup <- simple_flow
simple_flow <- backup 
   
#Replace the zones with the StabDen class
#https://stackoverflow.com/questions/7547597/dictionary-style-replace-multiple-items
map = setNames(LUT$LUT,LUT$zone_id)
simple_flow[,1]<- map[simple_flow[,1]]
simple_flow[,2]<- map[simple_flow[,2]]
View(head(simple_flow))

simple_flow_mat <- simple_flow
rm(simple_flow)

simple_flow <- data.frame()
simple_flow <- as.data.frame(simple_flow_mat[,c(1,2)] ) 
simple_flow$Count <- as.data.frame(as.numeric(simple_flow_mat[,3]))
simple_flow$Count <- simple_flow$Count$`as.numeric(simple_flow_mat[, 3])`

simple_flow$Count <- as.numeric(simple_flow$Count)
names(simple_flow ) <- c("O","D","Count")



#Drop all O & D that are not in EW
simple_flow <- simple_flow[which(!is.na(simple_flow$O)),]
simple_flow <- simple_flow[which(!is.na(simple_flow$D)),]



#sum the table ******************
now <- Sys.time()

  stabden<- simple_flow %>% 
  group_by(O,D) %>% 
  summarise(Frequency = sum(Count,na.rm = T))

difftime(Sys.time(), now)
stabden <- as.data.frame(stabden)




#Clean up the data frame 
a <- as.data.frame(str_split_fixed(as.character(stabden$O), pattern = "\\*", n = Inf))
names(a) <- c('O_Stab', 'O_Den', 'O_LAD','O_RG')
stabden <- cbind(stabden,a)

a <- as.data.frame(str_split_fixed(as.character(stabden$D), pattern = "\\*", n = Inf))
names(a) <- c('D_Stab', 'D_Den', 'D_LAD','D_RG')
stabden <- cbind(stabden,a)
rm(a)


#assign by year
stabden11<-stabden
rm(stabden)

#Sanity check
sum(simple_flow$Count, na.rm = T)
sum(stabden11$Frequency, na.rm = T)
#save(stabden11, file = "./_derived-data/flows_stabden11.RData")
#160275806
```


## 2001

```{r}
flow<- flow01
LUT <- LUT01

#Process the StabDen LUT
LUT$zone_id <- LUT$oa01cdo
LUT <- LUT[,c('zone_id','rdl_PSD','lad11nm','rgn11nm')]

LUT$LUT <- paste(LUT$rdl_PSD, "*", LUT$lad11nm, "*", LUT$rgn11nm)
LUT$LUT <- gsub(" ", "", LUT$LUT, fixed = TRUE)


#sum up the year specific breakdowns 
names(flow) <- c("O","D","Count")
simple_flow <- cbind(flow$O,flow$D, flow$Count)


#Replace the zones with the StabDen class
#https://stackoverflow.com/questions/7547597/dictionary-style-replace-multiple-items
map = setNames(LUT$LUT,LUT$zone_id)
simple_flow[,1]<- map[simple_flow[,1]]
simple_flow[,2]<- map[simple_flow[,2]]

simple_flow_mat <- simple_flow
rm(simple_flow)

simple_flow <- data.frame()
simple_flow <- as.data.frame(simple_flow_mat[,c(1,2)] ) 
simple_flow$Count <- as.data.frame(as.numeric(simple_flow_mat[,3]))
simple_flow$Count <- simple_flow$Count$`as.numeric(simple_flow_mat[, 3])`

simple_flow$Count <- as.numeric(simple_flow$Count)
names(simple_flow ) <- c("O","D","Count")


#Drop all O & D that are not in EW
simple_flow <- simple_flow[which(!is.na(simple_flow$O)),]
simple_flow <- simple_flow[which(!is.na(simple_flow$D)),]



#sum the table ******************
now <- Sys.time()

  stabden<- simple_flow %>% 
  group_by(O,D) %>% 
  summarise(Frequency = sum(Count,na.rm = T) )

difftime(Sys.time(), now)
stabden <- as.data.frame(stabden)
#Sanity check
#sum(simple_flow$Count, na.rm = T)
#sum(stabden11$Frequency, na.rm = T)



#Clean up the data frame 
a <- as.data.frame(str_split_fixed(as.character(stabden$O), pattern = "\\*", n = Inf))
names(a) <- c('O_Stab', 'O_Den', 'O_LAD','O_RG')
stabden <- cbind(stabden,a)

a <- as.data.frame(str_split_fixed(as.character(stabden$D), pattern = "\\*", n = Inf))
names(a) <- c('D_Stab', 'D_Den', 'D_LAD','D_RG')
stabden <- cbind(stabden,a)
rm(a)


#assign by year
stabden01<-stabden
rm(stabden)

#save(stabden01, file = "./_derived-data/flows_stabden01.RData")
```


## 1991

```{r}
flow<- flow91
LUT <- LUT91

#Process the StabDen LUT
LUT <- LUT[,c('zone_id','rdl_PSD','lad11nm','rgn11nm')]

LUT$LUT <- paste(LUT$rdl_PSD, "*", LUT$lad11nm, "*", LUT$rgn11nm)
LUT$LUT <- gsub(" ", "", LUT$LUT, fixed = TRUE)


#sum up the year specific breakdowns 
breakdowns <- c("Flow_1-15","Flow_16-29","Flow_30-44","Flow_44-PenAge","Flow_PenAge")
simple_flow <- cbind(flow$O_91_WD91CD,flow$D_91_WD91CD, rowSums(flow[,breakdowns]))


#Replace the zones with the StabDen class
#https://stackoverflow.com/questions/7547597/dictionary-style-replace-multiple-items
map = setNames(LUT$LUT,LUT$zone_id)
simple_flow[,1]<- map[simple_flow[,1]]
simple_flow[,2]<- map[simple_flow[,2]]

simple_flow_mat <- simple_flow
rm(simple_flow)

simple_flow <- data.frame()
simple_flow <- as.data.frame(simple_flow_mat[,c(1,2)] ) 
simple_flow$Count <- as.data.frame(as.numeric(simple_flow_mat[,3]))
simple_flow$Count <- simple_flow$Count$`as.numeric(simple_flow_mat[, 3])`

simple_flow$Count <- as.numeric(simple_flow$Count)
names(simple_flow ) <- c("O","D","Count")


#Drop all O & D that are not in EW
simple_flow <- simple_flow[which(!is.na(simple_flow$O)),]
simple_flow <- simple_flow[which(!is.na(simple_flow$D)),]



#sum the table ******************
now <- Sys.time()

  stabden<- simple_flow %>% 
  group_by(O,D) %>% 
  summarise(Frequency = sum(Count,na.rm = T))

difftime(Sys.time(), now)
stabden <- as.data.frame(stabden)
#Sanity check
#sum(simple_flow$Count, na.rm = T)
#sum(stabden$Frequency, na.rm = T)



#Clean up the data frame 
a <- as.data.frame(str_split_fixed(as.character(stabden$O), pattern = "\\*", n = Inf))
names(a) <- c('O_Stab', 'O_Den', 'O_LAD','O_RG')
stabden <- cbind(stabden,a)

a <- as.data.frame(str_split_fixed(as.character(stabden$D), pattern = "\\*", n = Inf))
names(a) <- c('D_Stab', 'D_Den', 'D_LAD','D_RG')
stabden <- cbind(stabden,a)
rm(a)


#assign by year
stabden91<-stabden
rm(stabden)

#save(stabden91, file = "./_derived-data/flows_stabden91.RData")
```



## 1981
 The flow exist only as 1991 old wards. I have 7 908 such places. The 1981 wards are 


```{r}
flow<- flow81
#three col, OD list
names(flow) <- c("Origins","X2","Destinations","X4","counts")
simple_flow <-as.matrix(flow[,c("X2","X4","counts")])


LUT <- LUT81
levels(LUT$rdl_PSD)[levels(LUT$rdl_PSD)=="5_V.High-Fix*2_Low"] <- "3_Average-Fix*2_Low"#City of London fluke
levels(LUT$rdl_PSD)[levels(LUT$rdl_PSD)=="5_V.High-Fix*3_Average"] <- "3_Average-Fix*3_Average"#City of London fluke
LUT <- droplevels(LUT)
LUT$LUT <- paste(LUT$rdl_PSD, "*", LUT$lad11nm, "*", LUT$rgn11nm)
LUT$LUT <- gsub(" ", "", LUT$LUT, fixed = TRUE)

LUT <- LUT[,c("name","label",'rdl_PSD','lad11nm','rgn11nm','LUT_WD91CD','LUT__WD91C','LUT')]
LUT <- merge( LUT, x_codes_2,
              by.x = 'label', by.y = 'WD81CD')
LUT <- merge( LUT, x_codes_1,
              by = "WD91CD")
LUT$zone_id <- LUT$LUT_WD91CD



#Replace the zones with the StabDen class
#https://stackoverflow.com/questions/7547597/dictionary-style-replace-multiple-items
map = setNames(LUT$LUT,LUT$zone_id)
simple_flow[,1]<- map[simple_flow[,1]]
simple_flow[,2]<- map[simple_flow[,2]]

simple_flow_mat <- simple_flow
rm(simple_flow)

simple_flow <- data.frame()
simple_flow <- as.data.frame(simple_flow_mat[,c(1,2)] ) 
simple_flow$Count <- as.data.frame(as.numeric(simple_flow_mat[,3]))
simple_flow$Count <- simple_flow$Count$`as.numeric(simple_flow_mat[, 3])`

simple_flow$Count <- as.numeric(simple_flow$Count)
names(simple_flow ) <- c("O","D","Count")


#Drop all O & D that are not in EW
simple_flow <- simple_flow[which(!is.na(simple_flow$O)),]
simple_flow <- simple_flow[which(!is.na(simple_flow$D)),]



#sum the table ******************
now <- Sys.time()

  stabden<- simple_flow %>% 
  group_by(O,D) %>% 
  summarise(Frequency = sum(Count,na.rm = T))

difftime(Sys.time(), now)
stabden <- as.data.frame(stabden)
#Sanity check
sum(simple_flow$Count, na.rm = T)
sum(stabden$Frequency, na.rm = T)



#Clean up the data frame 
a <- as.data.frame(str_split_fixed(as.character(stabden$O), pattern = "\\*", n = Inf))
names(a) <- c('O_Stab', 'O_Den', 'O_LAD','O_RG')
stabden <- cbind(stabden,a)

a <- as.data.frame(str_split_fixed(as.character(stabden$D), pattern = "\\*", n = Inf))
names(a) <- c('D_Stab', 'D_Den', 'D_LAD','D_RG')
stabden <- cbind(stabden,a)
rm(a)


#assign by year
stabden81<-stabden
rm(stabden)

save(stabden81, file = "./_derived-data/flows_stabden81.RData")
```


if(F){
LUT$zone_id <- LUT$LUT_WD91CD
length(intersect( simple_flow[,1], names(map) )) #681









###########################DEBUG######################################################
#possible matches:  "WD91CD", "LUT_WD91CD"

LUT$zone_id <- LUT$LUT_WD91CD
#LUT$zone_id <- LUT$`_WD91CDO`#One Obs only.

#intersect( LUT$zone_id ,a_flow$X2 ) #gives things in common 
#setdiff( a_flow$X2, LUT$zone_id) # in the first, but not the second

LUT$zone_id <- as.factor(LUT$LUT_WD91CD) #7 908
a_PSDLUT <- levels(as.factor(LUT$zone_id))
a_overlap <- as.factor( intersect( LUT$zone_id,a_flow$X2 ) )
a_missing <- levels(as.factor( setdiff( a_flow$X2, LUT$zone_id ) ))
a1_missing <-  levels(as.factor( setdiff(flow81$X2, LUT$zone_id ) ))

a_match = length(a_overlap )/length(a_PSDLUT)


LUT$zone_id <- as.factor(LUT$`_WD91CDO`) #9 290
b_PSDLUT <- levels(as.factor(LUT$zone_id))
b_overlap <- as.factor( intersect( LUT$zone_id,a_flow$X2 ) )
b_missing <- levels(as.factor( setdiff( a_flow$X2, LUT$zone_id ) ))
b_match = length(a_overlap )/length(a_PSDLUT)



###########################DEBUG
a <- as.factor( c(as.character(LUT81$rdl_PSD),as.character(LUT81$LUT_WD91CD) ) )

b1 <- as.factor(Reduce(setdiff, list(LUT$zone_id ,a_flow$X2)))
b2 <- as.factor(Reduce(setdiff, list(LUT$zone_id ,a_flow$X4))) 

b1f <- levels(as.factor(a_flow$X4)) #9 942
b2f <- levels(as.factor(a_flow$X2)) #14 757

a1f <- levels(as.factor(LUT$WD91CD) )
a2f <- levels(LUT$LUT_WD91CD)



#there are 7926 places combinaitions 
######################################################################################
}





```{r test}
# simple_flow1 <- simple_flow[1:10,]
# destination <- simple_flow1$D
# destination[1:5] <- "2_Low*5_Crowded*Camden*London"
# simple_flow1$D <- destination 
# 
# library(dplyr)
# ward91 <- simple_flow1 %>% 
#   group_by(O,D) %>% 
#   summarise(Frequency = sum(Count))
# 
# 
# sum(a[which(a$D == "2_Low*5_Crowded*Camden*London"),]$Frequency)
# sum(simple_flow1[which(simple_flow1$D == "2_Low*5_Crowded*Camden*London"),]$Count)
# 
# 
# sum(simple_flow1$Count, na.rm = T)
# sum(a$Frequency, na.rm = T)
```





#matrix: https://stackoverflow.com/questions/35956790/most-efficient-way-to-aggregate-matrix-based-on-grouping-variable

